Can diffusion alone explain brain-wide distribution of CSF tracers within 24 hours?

### 2019-07-05 tex/rev1/paper.tex
update

\textbf{}

@@

\subsection{Estimation of diffusion coefficients with a manufactored Solution.} 
We first ran a series of tests of different $\alpha$ and $\beta$ for the manufactured solutions where we assumed observations every 2.4 hours
over the course of 24 hours. It was found that for $\alpha \in (10^{-6}, 10^{-2}$ and $\beta\in(10^{-6}, 10^2)$, the error in 
the diffusion coefficients of both CSF, grey and white matter was less than 7\%. Furthermore,  
$\alpha \in (10^{-6}, 10^{-2}$ and $\beta\in(10^{-6}, 10^{-2})$ gave errors of less than 1\%. Second, the robustness with respect noise
was investigated. The noiseamplitude was set to 0.3 which equals the initial condition of the manufactured solution
and 23\% of the manufactured solution at its max. The method was found robust with respect to the noise, as illustrated in the Supplementary Fig~\ref{12hourswithnoise}.  In fact, for  $\alpha \in (10^{-6}, 10^{-2}$ and $\beta\in(10^{-6}, 10^{-2})$ the error in the diffusion coefficients in CSF was less than 23\% and less than 9.7\% in grey and white matter. \kam{Lars: skriv om resten av eksperimentene}

@@

\begin{figure}
\centering
\includegraphics[scale=0.35]{../Vent-2.png} 
\caption{ The images shows the ventricular wall at the same time points. The upper row shows the observations with following preprocessing left to right: Raw observations, projection of CSF value onto the boundary, Gaussian smoothing. The middle row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},1.0 ,1.0$). The bottom row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},100.0 ,100.$). }
\label{VENT}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.35]{../SAS-2.png} 
\caption{ The images shows the SAS boundary at the same time points. The upper row shows the observations with following preprocessing left to right: Raw observations, projection of CSF value onto the boundary, Gaussian smoothing. The middle row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},1.0 ,1.0$). The bottom row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},100.0 ,100.$). }
\label{SAS}
\end{figure}

>>>>

\textbf{MRI data.}

It can be seen from Fig XX that the boundary conditions is noise. This may be attributed to noise or small errors
in the segmentation/registration process where voxels close to the boundaries between the brain and CSF are miss-aligned
by the sub-voxel segementation procedure. In particular, the surfaces can cut a voxel at any plane, not only the planes
through the voxel vertices. We chose three approaches to handle this problem. \kam{Lars: kan du utbrodere litt her? 
Jeg synes vi skal beholde også Fig 10 fra tidligere.  }

@@

\subsection{Estimation of diffusion coefficients with a manufactored Solution.} 
We first ran a series of tests of different $\alpha$ and $\beta$ for the manufactured solutions where we assumed observations every 2.4 hours
over the course of 24 hours. It was found that for $\alpha \in (10^{-6}, 10^{-2}$ and $\beta\in(10^{-6}, 10^2)$, the error in 
the diffusion coefficients of both CSF, grey and white matter was less than 7\%. Furthermore,  
$\alpha \in (10^{-6}, 10^{-2}$ and $\beta\in(10^{-6}, 10^{-2})$ gave errors of less than 1\%. Second, the robustness with respect noise
was investigated. The noiseamplitude was set to 0.3 which equals the initial condition of the manufactured solution
and 23\% of the manufactured solution at its max. The method was found robust with respect to the noise, as illustrated in the Supplementary Fig~\ref{12hourswithnoise}.  In fact, for  $\alpha \in (10^{-6}, 10^{-2}$ and $\beta\in(10^{-6}, 10^{-2})$ the error in the diffusion coefficients in CSF was less than 23\% and less than 9.7\% in grey and white matter. Because of the much larger 
error in the CSF compartment, we decided to re-mesh with a focus on the grey and white. \kam{Lars: skriv om resten av eksperimentene. Fig 6 og 7 bor med i Suppl}

@@

\begin{figure}
\centering
\includegraphics[scale=0.35]{../Vent-2.png} 
\caption{ The images shows the ventricular wall at the same time points. The upper row shows the observations with following preprocessing left to right: Raw observations, projection of CSF value onto the boundary, Gaussian smoothing. The middle row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},1.0 ,1.0)$. The bottom row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},100.0 ,100.)$. }
\label{VENT}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.35]{../SAS-2.png} 
\caption{ The images shows the SAS boundary at the same time points. The upper row shows the observations with following preprocessing left to right: Raw observations, projection of CSF value onto the boundary, Gaussian smoothing. The middle row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},1.0 ,1.0)$. The bottom row shows the corresponding states with the regularization parameters $\alpha , \beta \gamma = (10\sp{-6},100.0 ,100.)$. }
\label{SAS}
\end{figure}
